Efficient ancestry and mutation simulation with msprime 1.0

### 2021-12-01 paper.tex
Fixup table 1

\begin{table}
{ % begin box to localize effect of arraystretch change
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{lp{12cm}}
Interface
& Separation of ancestry and mutation simulations.
Ability to store arbitrary metadata along with simulation
results, and automatic recording of provenance information
for reproducibility.
Jupyter notebook~\citep{kluyver2016jupyter} integration.
Rich suite of analytical and visualisation methods via \tskit\ library. \\

@@

\end{tabular}
}
\caption{\label{tab-v1-summary}Major features
of \msprime\ 1.0 added since version 0.3.0~\citep{kelleher2016efficient}.}
\end{table}

>>>>

\begin{table}
\small{
{ % begin box to localize effect of arraystretch change
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{lp{6.5cm}}
Interface
& Separation of ancestry and mutation simulations.
Ability to store arbitrary metadata along with simulation
results, and automatic recording of provenance information
for reproducibility.
Jupyter notebook~\citep{kluyver2016jupyter} integration.
Rich suite of analytical and visualisation methods via \tskit\ library. \\

@@

\end{tabular}
}
}
\caption{\label{tab-v1-summary}Major features
of \msprime\ 1.0 added since version 0.3.0 \citep{kelleher2016efficient}.}
\end{table}
